Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-23 manuscript/manuscript.Rmd
cant get the msy-escapement tuning figure to print out correctly

# Fishery management figures

```{r escapement_msy, fig.cap="TBD.", out.width = "6.5in"}
library(patchwork)
msy_rewards <- msy |>
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

@@

rmsy <- msy_rewards |>
  ggplot(aes(action, mean_reward, 
             ymin = mean_reward - 2*sd,
             ymax=mean_reward+2*sd)) +
  geom_point() + geom_ribbon(alpha=0.4) +
  labs(y = "episode reward", x = "constant mortality") +
  theme(aspect.ratio = 1/1)

@@

```{r state-space, fig.cap="TBD.", out.width = "6.5in"}
i_tac <- which.min(abs(actions - best_action * 0.8))

>>>>

```{r classical_tuning, fig.cap = "TBD. Red = MSY, Green = 80% TAC", out.width = "6.5in"}
library(patchwork)
msy_rewards <- msy |>
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

@@

rmsy <- msy_rewards |>
  ggplot(aes(action, mean_reward, 
             ymin = mean_reward - 2*sd,
             ymax=mean_reward+2*sd)) +
  geom_point() + geom_ribbon(alpha=0.4) +
  labs(y = "episode reward", x = "constant mortality") +
  theme(aspect.ratio = 1/1) + 
  geom_vline(aes(xintercept=0.0465), color="red") + 
  geom_vline(aes(xintercept=0.0370), color="green")

@@

```{r state-space, fig.cap="TBD.", out.width = "6.5in"}
i_tac <- which.min(abs(actions - best_action * 0.8))
actions[[i_tac]]
